\documentclass[10pt,a4paper,sans]{moderncv}

\usepackage[scale=0.9]{geometry}
\usepackage{multicol}

\moderncvstyle{classic}
\moderncvcolor{black}
\setlength{\hintscolumnwidth}{4cm}

\name{Igor}{Feofilaktov}
\title{Senior software engineer}
\email{feofilaktov.igor@gmail.com}
\mobile{+381 (63) 753-76-81}
\address{Cara Nikolaja II st, 69}{Belgrade, Serbia}

\begin{document}
    \makecvtitle

    \section{Work Experience}
        \cventry{Nov 2021 -- Present}{Yandex}{Senior software engineer}{Adevertising technologies}{QA\&Release infrastructure team}{
        Leading team of QA engineers tasked with providing regression and acceptance tests in production-like environment for advertising backend service.
		\begin{itemize}
			\item Designed the infarstructure for differential tests using real external services instead of stubs which helped to split monolith application into several microservices.
            \item Decreased testing service downtime by 20\% by organizing on-call duty process.
            \item Reduced resource utilization by tests by 30\% via various optimizations.
            \item Performed capacity planning and resource management for QA\&test infrastructure.
        \end{itemize}
    }
        \cventry{Apr 2018 -- Oct 2021}{Yandex}{Software engineer}{Adevertising technologies}{QA\&Release infrastructure team}{
        Developed reliable differential tests for the Ads engine with self-updating test data gathered from the production environment. 
        Improved QA\&Release processes:
		\begin{itemize}
			\item Triple the number of releases per week by automating the acceptance process.
			\item Increased accuracy of load differential tests by 2 times.
            \item Improved testing infrastructure stability and availability by setting up monitoring and alerting system.
		\end{itemize}
	}
        \cventry{Aug 2017 -- Apr 2018}{Yandex}{Software engineer}{Adevertising technologies}{Statistics infrastructure team}{
        Designed and implemented distributed system for availability monitoring of advertiser's websites. Decreased average reaction time from 24 hours to 1 hour.
	}
        \cventry{Dec 2016 -- Jul 2017}{New Cloud Technologies}{QA automation engineer}{Mail platform developing team}{}{
		Built automated testing framework from the ground up. Integrated QA processes into the CI/CD system.
		\begin{itemize}
			\item Wrote automated tests for service's API.
			\item Designed issue tracker workflows for bug tracking issues, feature requests and releases.
		\end{itemize}
	} 
        \cventry{Sep 2015 -- Nov 2016}{Search portal Sputnik}{QA automation engineer}{Mail developing team}{}{
		Automated functional and regression tests for service backend.
		\begin{itemize}
			\item Implemented automated tests for components of the system
			\item Designed and implemented web-service aimed to help the manual testers set up their test environment.
		\end{itemize}
	} 
        \cventry{May 2014 -- Aug 2015}{Internet-Initiatives Development Fund}{Tech support engineer}{IT team}{}{
		Solved wide range of problems including:
		\begin{itemize}
			\item Set up Zabbix monitoring system for network devices and prodiction services.
			\item Automated routine tasks such as parsing WEB-pages to organize data for easier analysis in MS Excel.
			\item Automated manual tests for company's website using Selenium web driver framework.
		\end{itemize}
	} 

    \section{Education}
        \cventry{2009-2014}{Specialist in Mathematics}{Lomonosov Moscow State University, Moscow, Russia}{}{}{}

    \section{Programming languages}{
        \cvcomputer{Advanced level:}{python}{Basic level:}{SQL, C++, Bash, Perl}
    }{}{}{}

    \section{Skills}{
        \cvcomputer{Testing tools}{pytest, allure}{VCS}{git, mercurial}
        \cvcomputer{Monitoring Tools}{zabbix, grafana,\newline Yandex internal monitoring systems}{Development Tools}{vim, ipython, gdb, UNIX tools}
        \cvcomputer{CI/CD}{Jenkins,\newline Yandex internal CI/CD system}{Other}{RESTful, RPC,\newline Microservice architecture}
    }{}{}{}

    \section{Languages}{
        \cvlanguage{Russian}{native}{}
        \cvlanguage{English}{high intermediate}{}
    }{}{}{}
\end{document}
